\subsubsection{PT8633 SDI Test pattern Generator, High-end}

\spectabular
\textbf{Connectors:}								& 2 x BNC\\
\textbf{Format:}										& 270 Mb/s component \\
																		& Complies with ITU-R BT 656 and SMPTE 259M \\
\textbf{Data format:}								& Scrambled NRZI 270 Mbit/s \\
\textbf{Output Impedance:}					& 75 \ohm \\
\textbf{Return loss:}								& $>$ 15 dB, 5 to 270 MHz\\
\textbf{Amplitude:}									& 800 mV $\pm$ 10\% \\
\textbf{Jitter:}										& $<$ 0.2 UI (one UI equals 3.7 ns) \\
\textbf{Timing range:}							& 525/60: $\pm$ 1 field \\
																		& 625/50: $\pm$ 1 field \\
\textbf{Timing resolution:}					& 37.5 ns (one half clock cycle on the 13.5 MHz clock) \\
\textbf{Ancillary data:}						& \\
\textbf{EDH:}												& ON/OFF \\
\textbf{Embedded audio:}						& \\
\textbf{Position:}									& Audio group 1, 2, 3 or 4 (only one group at a time), all channels in each group \\
\textbf{Output signals:}						& \\
																		& Stereo 800Hz, No click \\
																		& Stereo 1 kHz, No click \\
																		& Stereo EBU 1 kHz, Single click in Ch. A \\
																		& Stereo BBC 1 kHz, Single click in Ch.A and double click in Ch.B \\
																		& Mono EBU 1 kHz, Single click in both Ch. A and Ch. B \\
																		& Mono, No click \\
																		& Dual, 1 kHz in Ch. A, 400Hz in Ch. B, No Click \\
																		& Wordclock, 48 kHz \\
\textbf{Output levels:}							& Silence, 0, -9, -12, -15, -16, -18, -20 dBFS \\
\textbf{Preemphasis:}								& None \\
\end{tabular*}

\textbf{Output signals:}

\begin{itemize}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}

\item Colourbar
\item \textbf{525-lines NTSC:}
\begin{itemize}
\item SMPTE bar
\item FCC Colourbar
\item 75\% Colourbar, ITU 801 (timing and levels acc. to ITU801) \\
\item 100\% bar \\
\item Red 75\% \\
\end{itemize}
\item \textbf{625-lins PAL:}
\begin{itemize}
\item EBU bar
\item 75\% Colourbar, ITU 801 (timing and levels acc. to ITU801) 
\item 100\% bar
\item 75\% bar with grey
\item 75\% bar with red
\item Red, 75\%
\end{itemize}

\item Multiburst in Y,C\raisebox{-0.7ex}{B} and C\raisebox{-0.7ex}{R}
\item Luminance sweep
\item Y,C\raisebox{-0.7ex}{B} and C\raisebox{-0.7ex}{R} sweep
\item Multipulse
\item 15\% window
\item 20\% window
\item 100\% window
\item Flat field 100\%
\item black
\item Check field
\item Timing test
\item Field delay test
\item Bow-Tie
\item Digital/Analogue blanking markers
\item Digital grey
\item Field squarewave
\item Alternating black/white, 0.1 Hz
\item End-of-line pulses
\item End-of-line porches (ITU801):
\begin{itemize}
\item White
\item Blue
\item Red
\item Yellow
\item Cyan
\end{itemize}
\item Shallow ramp
\item Luminance ramp (black to white)
\item Limit ramp
\item Valid ramp
\item Staircase, 5 steps
\item Modulated staircase, 5 steps
\item Staircase, 10 steps
\item Pulse and bar
\item Yellow/grey ramp
\item Grey/blue ramp
\item Cyan/grey ramp
\item Grey/red ramp
\item C\raisebox{-0.7ex}{B},Y and C\raisebox{-0.7ex}{R}, Y ramp
\item Crosshatch
\item PLUGE
\item Safe area
\item CCIR18
\item CCIR17
\item CCIR330
\item CCIR331
\item VMT01 test pattern (only 625 lines)
\item Philips test pattern:
\begin{itemize}
\item 625 lines in 4:3 aspect ratio
\item 625 lines in 16:9 aspect ratio
\item 525 lines in 4:3 aspect ratio
\item 525 lines in 16:9 aspect ratio
\end{itemize}
\item FuBK test pattern:
\begin{itemize}
\item 625 lines in 4:3 aspect ratio
\item 625 lines in 16:9 aspect ratio
\end{itemize}
\end{itemize}

\textbf{Note:} The Philips test pattern can be configured in respect to:
\begin{itemize}
\item Moving bar ON/OFF
\item 5/10 step staircase
\item Anti-PAL ON/OFF
\item PLUGE ON/OFF
\item Corner circles ON/OFF (only 16:9)
\end{itemize}

%\textit{For detailed signal descriptions, please refer to Appendix XXX}

\paragraph{Source Identification:}
\spectabular
Standard signals:					& Three strings with up to 16 characters can be added to the signal \\
Philips and FuBK Pattern:	& Philips pattern \\
													& Text in upper and lower text area. Time and date inserted in centre part of crosshatch lines \\
\end{tabular*}

\paragraph{Output monitoring}
Continuous of output level with error flag on ``Change-over'' connector. Detector can be disabled.

