\paragraph{Status:Preset}
\display{HD-SD Preset Status \leftbutton \downbutton \rightbutton}{NO PRESET ACTIVE}
\display{HD-SD Preset Status \leftbutton \downbutton \rightbutton}{PRESET (1):name of preset}

\paragraph{Status: Genlock}
\display{Genlock:A \leftbutton \downbutton \rightbutton}{Signal:PAL Burst Status: GENLOCKED}
\display{Genlock:Internal \leftbutton \downbutton \rightbutton}{Signal:-------Status:-------}

The genlock status display shows the input selected for genlock and the format of genlock selected. If the signal is NTSC or PAL the display will also indicate whether sync lock or burst lock is being used.

\textbf{Status: Analogue test pattern generator}
\display{Analog TPG1:PLUGE \leftbutton \downbutton \rightbutton}{System:PAL w/PAL ID +TEXT}

The status display for the analogue test pattern generator shows the signal output from each the generator and the system selected. If the text or time clock is inserted into the test pattern, then the presence is shown.

\textbf{Status: SDI test pattern generator}
\display{SDI-TPG1:PLUGE \leftbutton \downbutton \rightbutton}{System:525/59.94.+TEXT +AUDIO +EDH}

The status display for serial digital test pattern generator shows the signal output from each generator and the system selected. Also the status for text (and clock), embedded audio, and EDH inserted into test signals/pattern is shown.

\textbf{Status: SDI Basic generator}
\display{SDI-TSG3:WINDOW 15\% \leftbutton \downbutton \rightbutton}{System:525/59.94. +AUDIO +EDH}

The serial digital test signal generator status display shows the signal output from each of the Basic SDI generators and the system selected. Also the status for embedded audio and EDH is shown. No text or clock can be inserted.

\textbf{Status: AES/EBU Audio Generator}
\display{AES/EBU1:Stereo EBU 1kHz \leftbutton \downbutton \rightbutton}{Level:-9dBFS Timing:PAL}

The status display for the AES/EBU digital audio generator shows the output signal and level of the audio. The five NTSC phases or the PAL timing phase is also displayed.

\textbf{Status: DATE-TIME}
\display{DATE:05-02-02 TIME:14:05:05 ?? \leftbutton \downbutton \rightbutton}{REF: VITC Code STATUS: LOCKED}
This display shows the current status of date and time i.e. the information inserted into the video signal.

\textbf{Status: WARNING}
\display{HD-SD Error/Warning Status:?? \leftbutton \downbutton \rightbutton}{No error detected}
\display{HD-SD Error/Warning Status:?? \leftbutton \downbutton \rightbutton}{No active warning}
\display{HD-SD Error/Warning Status:?? \leftbutton \downbutton \rightbutton}{E(00n):mmmmmmmmmm}

The display shows the error/warnings status. The ``No error detector'' shows that no errors has been detected. The ``No active warning'' shows that no errors are present, but previously detected errors are stored in the ``Errorqueue''. In case of an error condition, the error number is shown in the display.
%\textit{Please refer to Appendix xxx for explanation of error messages}
